ECE498:~Senior Capstone Project I\\\textbf{\underline{Project Proposal}}\\ \vspace{0.5in} Project Title: Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle \vspace{1.0in} \author{Hannah Grady and Nicholas Nauman\\ Advisor: Dr.~Suruz Miah}

### 2021-10-28 proposal.tex
Updated proposal.tex with system ID section

y(t) + a_1y(t - 1) +...+a_{na}y(t - n_{a}) = b_{1}u(t-n_{k})+...+b_{nb}u(t - n_{k}-n_{b}+1) + e(t)

y(t) is the output of the equation at a certain time t, while u(t) is the input at a certain time t. The noise disturbance of the system is represented by e(t). The variables na, nb, and nk are the system’s number of poles, amount of b parameters, and the samples before the inputs begin to affect the system’s output.

>>>>

$y(t) + a_1y(t - 1) +...+a_{na}y(t - n_{a}) = b_{1}u(t-n_{k})+...+b_{nb}u(t - n_{k}-n_{b}+1) + e(t)$

$y(t)$ is the output of the equation at a certain time t, while u(t) is the input at a certain time t. The noise disturbance of the system is represented by e(t). The variables na, nb, and nk are the system’s number of poles, amount of b parameters, and the samples before the inputs begin to affect the system’s output.

\section{System Identification}

Introduction to system identification...., Mathworks' MATLAB has the system
identification toolbox, where a few existing examples demonstrate the working principle of this toolbox.

\subsection{Example 1: ..........}
\label{sec:sysID-Example1}

\subsection{Example 2: ..........}
\label{sec:sysID-Example2}

\subsection{Example 3: ..........}
\label{sec:sysID-Example3}
